%!TEX root = ../olga-cv.tex
%----------------------------------------------------------------------------------
%            Awards
%----------------------------------------------------------------------------------
\section{Awards}
\cvitem{2015}{LLNL Deputy Director's for Science and Technology (DDS\&T) Excellence in Publication Award for work in load balancing.}
\cventry{2009-2014}{\href{https://lawrence-scholar-program.llnl.gov}{Lawrence Scholar Program (LSP) Fellowship}}{Lawrence Livermore National Laboratory}{}{}
 	{{\em Technical Supervisor:} Bronis R. de Supinski, Ph.D.}	
\cvitem{2006-2009}{\textbf{\href{http://www.nsfgrfp.org/}{NSF Graduate Research Fellowship}}, Texas A\&M University.}
\cvitem{2004-2007}{\textbf{\href{http://www2.ed.gov/programs/gaann/index.html}{GAANN Fellowship}}, Texas A\&M University.}
\cvitem{2004-2005}{Association of Former Students Fellowship, Texas A\&M University.}
\cvitem{2007-2011}{Broader Engagement grant recipient, Supercomputing Conference.}
\cvitem{2007}{Award to attend CRA-W/CDC Programming Languages Workshop.}
\cvitem{2005-2007}{Award to attend and speak at CRA-W Grad Cohort, Computing Research Association.}
\cvitem{2004}{Award to attend Grace Hopper Conference and DMP reunion, Computing Research Association.}
\cvitem{2003,2004}{\textbf{\href{https://parasol.tamu.edu/dreu}{Distributed Mentor Project}}; Computing Research Association.}
\cvitem{2004}{Outstanding Senior in Computer Science; Western Oregon University.}
\cvitem{2003}{Outstanding Achievement in Computer Science, Outstanding Achievement in Mathematics.}	
\cvitem{2003}{Who's Who Among Students in American Colleges and Universities, Phi Kappa Phi member.}
\cvitem{1997}{\textbf{\href{http://exchanges.state.gov/youth/programs/flex.html}{Future Leaders Exchange Program}}; one of one hundred recipients nationwide.\newline 
	U.S. Department of State, Freedom Support Act.}
