%!TEX root = ../olga-cv.tex
%----------------------------------------------------------------------------------
%            Teaching
%----------------------------------------------------------------------------------
	\cventry{2015-present}{Student Research Mentoring}{Lawrence Livermore National Laboratory}{}{}{
		\begin{itemize}
		\item (Spring 2022 - Present) Advisor, Michael McKinsey, CS major (Masters), Texas A\&M University.
		  Worked on multi-dimensional data composition for \href{https://thicket.readthedocs.io/en/latest/}{Thicket}.
		\item (Summer 2021 - Present) Committee member, Daryl Hawkins, NUEN major (PhD), Texas A\&M University.
		  Worked on novel transport algorithms.  Analyzed performance of MARBL on AWS.	
	         \item (Summer 2020 - Present) Committee member, Connor Scully-Allison, CS major (PhD), University of Arizona.
	          Working on interactive visualization for \href{https://thicket.readthedocs.io/en/latest/}{Thicket}.
		  Worked on interactive visualization for \href{https://llnl-hatchet.readthedocs.io/en/latest/}{Hatchet}.
		  Optimized \href{https://llnl-hatchet.readthedocs.io/en/latest/}{Hatchet},
        		  a call-tree based tool for performance analysis of HPC applications.
	        \item (Spring 2020 - Present) Ian Lumsden, CS major (PhD), University of Tennessee.
		  Working on a query language for \href{https://llnl-hatchet.readthedocs.io/en/latest/}{Hatchet},
        		  a call-tree based tool for performance analysis of HPC applications.
		\item (Fall 2019 - Present) Bengisu Elis, CS major (PhD), Technical University of Munich, Germany.
		  Working on research directions for MPI on heterogeneous architectures.
		\item (Fall 2019 - Summer 2023) Committee member, Suraj Kesavan, CS major (PhD), University of California Davis.
		    Working on research directions for performance visualization.
		\item (Spring 2022 - Spring 2023) Committee member, Vanessa Lama, CS major (Masters), University of Tennessee.
		  Worked on metadata for \href{https://thicket.readthedocs.io/en/latest/}{Thicket}.
	         \item (Spring 2022 - Spring 2023) Internship mentor, Treece Burgess, CS major (Masters), University of Tennessee.
		  Worked on statistics operations for \href{https://thicket.readthedocs.io/en/latest/}{Thicket}.  
		\item (Summer 2022) Internship mentor, Garrett Hooten, CS major (Bachelors), University of Tennessee Chattanooga.
		  Worked on instrumenting ExaMPI with Caliper and performance analysis.  
		\item (Summer 2021) Internship mentor, Gerald Collom, CS major (PhD), University of New Mexico.
		  Worked on persistent and partitioned MPI for heterogeneous architectures.		
	        \item (Summer 2020) Internship mentor, Kawthar Shafie Khorassani, CS major (PhD), The Ohio State University.
		  Worked on GPUDirect Async Designs with MVAPICH2-GDR.
        		\item (Summer 2020) Internship mentor, Katy Williams, CS major (PhD), University of Arizona.
		  Interactive tree visualization for \href{https://llnl-hatchet.readthedocs.io/en/latest/}{Hatchet},
	          a call-tree based tool for performance analysis of HPC applications.	          
		\item (Summer 2018 and 2019) Internship mentor, David Eberius, CS major (PhD), University of Tennessee.
		  Ported \href{http://www.exmatex.org/comd.html}{CoMD}, an ExMatEx proxy application to
		  \href{https://github.com/LLNL/RAJA}{RAJA}, to GPUs.
		  Load balancing metrics for GPUs.
		\item (Summer 2018) Internship mentor, Kewen Meng, CS major (PhD), University of Oregon.
		  Ported \href{http://www.exmatex.org/comd.html}{CoMD}, an ExMatEx proxy application to
		  \href{https://github.com/LLNL/RAJA}{RAJA}, to GPUs.
		\item (Summer 2016) Internship mentor, Hadia Ahmed, CS major (PhD), University of Alabama at Birmingham.
		  Performance impact of dynamic load imbalance on modified 
		  \href{http://www.exmatex.org/comd.html}{CoMD}, an ExMatEx proxy application.
		\item (Summer 2015) Internship mentor, Rasmus Larsen, CS major (MS), University of Copenhagen. %   \hfill {\em Summer 2015}\\
		  Enabled overdecomposition and dynamic work redistribution in
		  \href{http://www.exmatex.org/comd.html}{CoMD}, an ExMatEx proxy application.
		  Implemented a mechanism to introduce initial and dynamic load imbalance.
		\end{itemize}
	}
	\cventry{2007}{Student Team Mentoring}{Cluster Challenge}{ACM/IEEE Supercomputing Conference (SC)}{}{
		\begin{itemize}
		\item Mentored teams participating in the challenge, provided technical expertise in parallel performance and
			parallel applications ported by the teams to their clusters during the challenge.
		\end{itemize}
		}
	\cventry{2005-2009}{Student Research Mentoring}{Texas A\&M University}{}{}{
		\begin{itemize}
		\item Jeremy Vu, CSE major, Texas A\&M University. %   \hfill {\em Spring 2009}\\
			Worked on parallel algorithms in STAPL.
		\item Harshvardhan, CS major, %\hfill {\em Fall 2005 -- Spring 2007}\\
			%University Undergraduate Research Fellow,
			Texas A\&M. %, graduated December 2008.
			Worked on STAPL Graph, Dynamic Graph Composition Library.
		\item Kelli Bacon, CRA-W DMP Program. CE major, Gonzaga U. %  \hfill {\em Summer 2006} \\
			Dynamic Graph Composition Library.
		\item Saransh Mittal, CSE major, %   \hfill {\em Summer 2006} \\
			Indian Inst. of Technology, Bombay.
			Dynamic Graph Composition Library.
		\item Anna Tikhonova, CRA-W DMP Program. CS major, U. of San Francisco. %   \hfill {\em Summer 2005} \\
			%Currently a Ph.D. student at University of California - Davis.\\
			Parallel algorithms in STAPL.
		\end{itemize}
		}
	\cventry{2006}{Fellow}{Graduate Teaching Academy}{Texas A\&M University}{}{}

	\cventry{2006}{Student Mentoring Award}{Aggie Women in Comp. Science ({AWICS})}{Texas A\&M University}{}{}

%	\cventry{2002-2004}
%		{Teaching Assistant}{\href{http://www.wou.edu/las/natsci_math/math/}{Department of Mathematics}}{Western Oregon University}{}{}
%		%{Assisted a Math professor in grading, lecturing.}
%
%	\cventry{2002-2004}
%		{Tutor}{\href{http://www.wou.edu/las/cs/index.php}{Dept. of Computer Science} and \href{http://www.wou.edu/las/natsci_math/math/}{Dept. of Mathematics}}{Western Oregon University}{}{}
%		%{Tutored for various Computer Science and Math classes.}
%
%	\cventry{2001-2004}{Youth Mentor}{HOST Youth and Family Program}{Northwest Human Services}{}{}
