%!TEX root = ../olga-cv.tex
%----------------------------------------------------------------------------------
%            Professional Activities
%----------------------------------------------------------------------------------

%\begin{wrapfigure}{R}{1.1in}
%    \vspace{5.5em}
%	\scriptsize{\begin{tabular}{|p{.3in}|r|}
%		  %SC & Steering Cmte.\\
%		  %OC & Organizing Cmte.\\
%		  PC & Program Cmte.\\
%		  R  & Reviewing \\
%		  SV & Student Volunt.
%		  \end{tabular}}
%\end{wrapfigure}


\section{Conferences \& Workshops Organized}
	\cventry{2019-Present}{Salishan Conference on High Speed Computing}{Co-Chair}{}{}
		{Conference on computer architecture, languages, and algorithms organized by the tri-labs (LLNL, LANL, Sandia). 150+ attendees.}
	\cventry{2018-Present}{Nuclear Explosives Code Development Conference (NECDC)}{Co-Chair}{}{}
		{%Biennial meeting sponsored by the National Nuclear Security Administration (NNSA) of the United States Department of Energy (DOE) focuses on
		%issues relevant to the nuclear weapons code developer community, specifically
		Fundamental and applied research topics related to %the
		computational simulation. 300+ attendees.}
		% of nuclear weapons and effects.}
	\cventry{2018-Present}{JOWOG 34 Applied Computer Science (ACS)}{Co-Chair}{}{}
		{Scalable algorithms \& simulation techniques for LLNL, LANL, Sandia (US) and AWE (UK). 150+ attendees.}
	\cventry{2018}{Students@SC Program at ACM/IEEE Supercomputing Conference (SC)}{Vice-chair}{}{}
		{Organized 2-day program for undergraduate and graduate students at SC. 200+ attendees.}


\section{Committees}

%%%\cvitem
%%%{\bf Team Mentor}, Cluster Challenge, Supercomputing 2012 (SC'12) \hfill {\em 2012}
%%


	\cventry{2019-2021}{Lawrence Livermore National Laboratory (LLNL)}{Labwide Laboratory Directed Research and Development (LW LDRD) Committee Member}{}{}{}
	\cventry{2021}{International Conference on Supercomputing (ISC)}{Chair, Ph.D. Forum}{}{}{}
	\cventry{2020,2021}{IEEE International Parallel \& Distributed Processing Symposium (IPDPS)}{Programming Models and Compilers Papers Committee Member}{}{}{}
	\cventry{2020}{ACM/IEEE Supercomputing Conference (SC)}{Performance Papers Committee Member}{}{}{}
    \cventry{2020}{EuroMPI}{Technical Papers Committee Member}{}{}{}
	\cventry{2019,2020}{IEEE Cluster}{Programming and System Software Papers Committee Member}{}{}{}
    \cventry{2020}{Journal of Concurrency and Computation}{Reviewer}{}{}{}
	\cventry{2020}{International Conference on Supercomputing (ISC)}{Vice-Chair, Ph.D. Forum}{}{}{}
	\cventry{2020}{International Conference on Supercomputing (ISC)}{Tutorials Committee Member}{}{}{}
	\cventry{2015-2019}{Lawrence Livermore National Laboratory (LLNL)}{Computation Directorate representative on Livermore Graduate Scholar Program (LGSP) Committee}{}{}{}
	\cventry{2015,2019}{ACM/IEEE Supercomputing Conference (SC)}{Research Posters Committee Member}{}{}{}
	\cventry{2019}{Lawrence Livermore National Laboratory (LLNL)}{Science and Technology Awards Committee}{}{}{}
	\cventry{2019}{International Conference on Supercomputing (ISC)}{Ph.D. Forum Committee Member}{}{}{}
	\cventry{2019}{IEEE International Parallel \& Distributed Processing Symposium (IPDPS)}{Multidisciplin}{}{}{}
	\cventry{2019}{Journal of Signal Processing Systems}{Reviewer}{}{}{}
	\cventry{2018}{International Conference on Parallel Processing (ICPP)}{Chair of the Software Track}{}{}{}
	%\cventry{2018}{ACM/IEEE Supercomputing Conference (SC)}{Vice-chair of Students@SC}{}{}{}
	\cventry{2010,2011,2018}{ACM/IEEE Supercomputing Conference (SC)}{Tutorials Committee Member}{}{}{}
	%\cventry{2018}{Nuclear Explosives Code Development Conference (NECDC)}{LLNL POC}{}{}{}
	\cventry{2018}{IEEE International Conference on Cluster Computing (Cluster)}{System Software Track}{}{}{}
	\cventry{2018-present}{Parallel Computing Journal}{Reviewer}{}{}{}
	\cventry{2018}{IEEE International Parallel \& Distributed Processing Symposium (IPDPS)}{Progr. Models}{}{}{}
	\cventry{2018}{IEEE/ACM Intl Conf Cluster, Cloud, \&Grid Computing (CCGrid)}{Perf. Modeling \& Eval}{}{}{}
	\cventry{2017}{EuroMPI/USA 2017}{Research Posters Program Committee}{}{}{}
	\cventry{2017}{ACM/IEEE Supercomputing Conference (SC)}{Perf. Measurement, Modeling, and Tools}{}{}{}
	\cventry{2017}{IEEE International Conference on Cluster Computing (Cluster)}{Apps, Algos, \& Libraries}{}{}{}
	\cventry{2017}{International Conference on Parallel Processing (ICPP)}{Software}{}{}{}
	\cventry{2017}{IEEE International Parallel \& Distributed Processing Symposium (IPDPS)}{Software}{}{}{}
	\cventry{2016,2017}{Grace Hopper Conference}{Computer Systems Engineering}{}{}{}
	\cventry{2015}{ACM/IEEE Supercomputing Conference (SC)}{
		BoF: Progr. Languages, Models, \& Compilers}{}{}{}
	\cventry{2011}{Small Business Innovation Research (SBIR)}{DOE Office of Science Grant Review}{}{}{}
	\cventry{2011}{ACM/IEEE Supercomputing Conference (SC)}{Student Cluster Challenge}{}{}{}
	\cventry{2008}{ACM/IEEE Supercomputing Conference (SC)}{Broader Engagement}{}{}{}
