%!TEX root = ../olga-cv.tex
%----------------------------------------------------------------------------------
%        Research Experience
%----------------------------------------------------------------------------------
\section{Research Experience}
	\cventry{2014-present}
		{\href{http://www.llnl.gov}{Lawrence Livermore National Laboratory}}{Computer Scientist}{}{}
		{\begin{itemize}
		\item Developing techniques and tools for analyzing and optimizing performance of large scale multiphysics simulations on homogeneous and heterogeneous architectures. 
		\item Developing techniques and tools for load balancing scientific applications. 
		\item Developing parallel programming models and tools.
		\item Developing communication techniques for heterogeneous architectures.
		\item LLNL application point of contact for CORAL1 and CORAL2 Tools Working Groups.
		\item LLNL application point of contact for CORAL1 and CORAL2 Messaging Working Groups.
		\item Principal Investigator for the Performance Analysis and Visualization at Exascale (\href{https://computing.llnl.gov/projects/pave-performance-analysis-visualization-exascale}{PAVE}) Project
		\end{itemize}}
		
	\cventry{2009-2014}
		{\href{http://www.llnl.gov}{Lawrence Livermore National Laboratory}}{Lawrence Scholar}{}{}
		%{Developing a framework for asynchronous scalable correction of application load imbalance}
		{\begin{itemize}
            \item Developed a model enabling the comparison of and selection among
                  balancing algorithms for a specific state of a simulation.
            \item Developend a framework for decoupling and offloading the load balance computation,
                  enabling lazy load balancing.
            \item Developed an accurate and fast method to evaluate and balance the load in N-Body simulations
                  with highly non-uniform density, based on adaptive sampling.
			%\item Developed an application-independent load model and metrics;
			%\item Developed an algorithmic methodology for deciding {\em when} and {\em how} to correct application imbalance;
			%\item Developed a fast and accurate method of assigning and load balancing interactions in N-body applications;
			%\item Developed a framework for decoupling load balance algorithm resources from the application;
			%\item Developed a framework for offloading \& overlapping load balance computation with application execution;
			%\item Applied work to several large physics applications at LLNL.
		\end{itemize}}

	\cventry{2004-2009}
		{\href{http://www.cse.tamu.edu/}{Texas A\&M University, Department of Computer Science}}{Research Assistant}{}{}
		{\begin{itemize}
			\item Worked on distributed data structures in the Standard Template Adaptive Parallel Library (STAPL),
				a parallel superset of the C++ Standard Template Library. Implemented and optimized a parallel vector.
			\item Designed and implemented a set of parallel algorithms for STAPL.
				Assisted in development of the adaptive algorithm selection framework for STAPL.
			\item Explored the idea of lock-free containers for multi-threaded programming.
			%\item Working on a general scheduler and partitioner for STAPL, which will
			%be used to schedule and load-balance various applications using STAPL.
			\item Worked on a Dynamic Graph Composition Library for updating graph metrics of large, dynamic graphs.
		\end{itemize}}

	\cventry{May-Oct 2007,\\July-Aug 2008}
		{\href{http://www.llnl.gov}{Lawrence Livermore National Laboratory}}{Research Intern}{}{}
		{Worked on load balancing a multi-physics simulation via domain repartitioning
		and domain replication.  Devised techniques to cheaply estimate processor loads and decide
		when a load imbalance needs to be corrected.  Incorporated multi-constraint
		repartitioning (data parallelism) and domain replication (task parallelism)
		as a way to correct imbalance.
		}

	\cventry{Summer 2003,\\Summer 2004}
		{\href{http://www.cse.tamu.edu/}{Texas A\&M University, Department of Computer Science}}{Undergraduate Research Intern}{}{}
		{Designed and implemented a parallel array data structure and multiple
		parallel algorithms for the Standard Template Adaptive Parallel Library
		(STAPL), a parallel library for C++, superset of STL.}
